{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-22 thesis/quicksand.tex
rename quicksand motivation/pps section

This chapter presents Quicksand,
an execution framework for model checking to manage this trade-off at run-time.
Given a fixed CPU budget,
representing the user's patience for testing,
Quicksand dynamically alters its preemption strategy based on data race analysis
(\cite{tsan,fasttrack}, \cref{sec:landslide-datarace})
and optimizes the size of state spaces on the fly,
guided by state space estimation
(\cite{estimation}, \cref{sec:landslide-estimate}),
to best match that budget.
I will discuss the trade-off inherent in number of preemption points used (\cref{sec:quicksand-pps}),
introduce {\em Iterative Deepening},
the algorithm that Quicksand uses to automatically navigate that trade-off
(\cref{sec:quicksand-id}),
prove its soundness relative to the more expensive full verification approach
(\cref{sec:quicksand-soundness}),
and present a large evaluation of Quicksand against several
state-of-the-art approaches % implemented under Landslide
in which Quicksand performs best on both bug-finding and verification
(\cref{sec:quicksand-eval}).
% justifying the claim that model checkers should navigate said tradeoff at runtime
}

@@

\section{Preemption points}
\label{sec:quicksand-pps}

@@

\subsection{Types of preemption points} % TODO: find better name for sec'n

@@

\subsection{Terminology}

>>>>

This chapter presents Quicksand,
an execution framework for model checking to manage this trade-off at run-time.
Given a fixed CPU budget,
representing the user's patience for testing,
Quicksand dynamically alters its preemption strategy based on data race analysis
(\cite{tsan,fasttrack}, \cref{sec:landslide-datarace})
and optimizes the size of state spaces on the fly,
guided by state space estimation
(\cite{estimation}, \cref{sec:landslide-estimate}),
to best match that budget.
I will discuss the trade-off inherent in number of preemption points used
(\cref{sec:quicksand-motivation}),
introduce {\em Iterative Deepening},
the algorithm that Quicksand uses to automatically navigate that trade-off
(\cref{sec:quicksand-id}),
prove its soundness relative to the more expensive full verification approach
(\cref{sec:quicksand-soundness}),
and present a large evaluation of Quicksand against several
state-of-the-art approaches % implemented under Landslide
in which Quicksand performs best on both bug-finding and verification
(\cref{sec:quicksand-eval}).
% justifying the claim that model checkers should navigate said tradeoff at runtime
}

@@

\section{Motivation}
\label{sec:quicksand-motivation}

@@

\subsection{Preemption points}
\label{sec:quicksand-pps}

@@

\subsection{Terminology}
\label{sec:quicksand-terminology}
